What We Eval in the Shadows

### 2021-04-14 paper/main.tex
Usage

>>>>

\mypara{Discussion.} % more...

\eval is a powerful tool and can be sometimes with functions with more specialized goals. For instance, variable lookup in any environment can be performed with \c{get}. Building a call and executing can be done with \c{do.call}. Nevertheless, \eval shines when expressions passed to it can be of many different types. % And it is shorter to type, and no need to remember all the specialized functions.
